---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarizedata2 Package Description

<!-- badges: start -->

<!-- badges: end -->

The function summarize_data intends to calculate the median, mean, and standard deviation (sd) under certain grouping condition in a dataset. An na.rm argument is used to indicate if missing value (NA) should be removed or not from the data.

**Please note** that the package is named as"summarizedata2" to differentiate from another student's package with "summarizedata" in Stat545 repo

## Installation

You can install the development version of summarizedata from [GitHub](https://github.com/) with:

``` r
# 
devtools::install_github("stat545ubc-2024/summarizedata2")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#devtools::install_github("stat545ubc-2024/summarizedata2")
library(summarizedata)
library(palmerpenguins)# used penguin data to demonstrate the example 
summarize_data(penguins,species,island,summ_vars=bill_length_mm,na.rm=TRUE)
summarize_data(penguins,sex,island,summ_vars=bill_depth_mm,na.rm=TRUE)
## basic example code
```
